Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems

### 2024-08-07 article.hid2-ub-cicd.ppam24.tex
fix tex
#1
up format
#1

\usepackage{url}
\usepackage{tikz}
\usepackage{xcolor}
\definecolor{darkred}{rgb}{0.6, 0, 0}
\definecolor{darkgreen}{rgb}{0, 0.5, 0}
\definecolor{darkblue}{rgb}{0, 0, 0.5}
\definecolor{darkmagenta}{rgb}{0.5, 0, 0.5}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,      % Enable colored links
    linkcolor=darkred,    % Color for internal links
    filecolor=darkgreen,  % Color for file links
    urlcolor=darkblue,    % Color for external URLs
    citecolor=darkmagenta % Color for citations
}

\usepackage{ifthen}

\newcommand{\imagedir}{./} % default directory
% Shell command to check if a directory exists
\immediate\write18{if [ -d "./images" ]; then echo "\\\\renewcommand{\\imagedir}{./images/}"; fi > checkdir.tex}

% Input the output commands from the shell
\InputIfFileExists{checkdir.tex}{}{}

@@

\title{Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems}
\author{}
\author{Luca Berti\inst{1} \and Vincent Chabannes \inst{1}\orcidID{0009-0005-3602-3524} \and
Javier Cladellas \inst{1}\orcidID{0009-0003-8687-7881} \and 
Abdoulaye Diallo \inst{1}\orcidID{0009-0006-8731-0547}\ \and
Maryam Maslek Elayam \inst{1}\orcidID{0000-0003-0880-5180} \and
Philippe Pinçon \inst{1}\orcidID{0009-0009-7724-3055 } \and
Christophe Prud'homme\inst{1}\orcidID{0000-0003-2287-2961}}
\institute{Cemosis, IRMA UMR 7501, University of Strasbourg, CNRS\\ 
\email{\{vincent.chabannes,christophe.prudhomme\}@cemosis.fr}}

\authorrunning{V. Chabannes et al.}

@@

\section{Introduction}
The building sector accounts for approximately 40\% of final energy consumption and 36\% of greenhouse gas emissions within the European Union~\cite{european_commision_energy_2020}. In response, the EU has established ambitious targets under the Horizon 2050 framework to double energy renovation rates over the next decade~\cite{european_commision_stakeholder_2021}, highlighting the need for innovative solutions to drive these initiatives forward. The Centre of Excellence (CoE) HiDALGO2 project, focusing on high-performance computing and advanced simulations, is at the forefront of tackling this challenge, mainly through its Urban Building pilot application.

@@

\section{Ktirio Urban Building Workflow}

@@

\subsection{Data Handling and Simulation Process}
The workflow begins with collecting and preparing GIS and weather data, transforming it into a format usable for simulations. This data is then partitioned for scalable processing and converted into Modelica and Feel++\cite{christophe_prudhomme_feelppfeelpp_2024} compatible formats through the UBEM Generator.

@@

\subsection{Final Analysis and Urban Scale Energy Evaluation}
The final step involves the UBEM Simulator, which generates large-scale outputs that summarize the overall energy consumption and environmental impact of buildings on an urban scale. This comprehensive urban scale analysis merges data from the building energy and air quality models to provide a holistic view of urban environmental quality.

@@

\section{Overview of Urban Building Modeling and Simulation}

>>>>

\usepackage{url}
\usepackage{tikz}
\usepackage{xcolor}
\definecolor{darkred}{rgb}{0.6, 0, 0}
\definecolor{darkgreen}{rgb}{0, 0.5, 0}
\definecolor{darkblue}{rgb}{0, 0, 0.5}
\definecolor{darkmagenta}{rgb}{0.5, 0, 0.5}
\usepackage{hyperref}

\IfFileExists{.git/gitHeadInfo.gin}{
    \usepackage[pcount,grumpy,mark,markifdirty]{gitinfo2}
}{%
    \usepackage[local,pcount,grumpy,mark,markifdirty]{gitinfo2}
}

%% By default, llncs tocdepth value is 0, so only chapters and parts are shown in the ToC, but no sections and deeper levels of structure.
%% If \setcounter{tocdepth}{1} is used, the sections show up in the ToC.
%% I suggest to use \usepackage{tocbibind} in order to add the LoF and LoT in the ToC as well, if the ToC should not be listed itself, use \usepackage[nottoc]{tocbibind} instead.
%% As long as no figure or table environments with \caption commands or explicit \addcontentsline{lof}{...}{...} etc. are used, the LoF and LoT are empty of course.
\setcounter{secnumdepth}{4}
\setcounter{tocdepth}{1}
\usepackage[section,notlof,notlot,nottoc,]{tocbibind}

\title{Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems}
\author{Luca Berti\inst{1} \and Vincent Chabannes \inst{1}\orcidID{0009-0005-3602-3524} \and
Javier Cladellas \inst{1}\orcidID{0009-0003-8687-7881} \and 
Abdoulaye Diallo \inst{1}\orcidID{0009-0006-8731-0547}\ \and
Maryam Maslek Elayam \inst{1}\orcidID{0000-0003-0880-5180} \and
Philippe Pinçon \inst{1}\orcidID{0009-0009-7724-3055 } \and
Christophe Prud'homme\inst{1}\orcidID{0000-0003-2287-2961}}
\institute{Cemosis, IRMA UMR 7501, University of Strasbourg, CNRS\\ 
\email{\{vincent.chabannes,christophe.prudhomme\}@cemosis.fr}}
\date{\gitReln\  \gitAuthorDate\ (\gitAbbrevHash)}
\authorrunning{V. Chabannes et al.}

% Define custom color
\definecolor{CustomBlue}{rgb}{0.25, 0.41, 0.88} % RoyalBlue
% Set up hyperref with the custom citecolor
\hypersetup{
    pdftitle={\@title},
    pdfauthor={\@author},
    pdfsubject={\@subject},
    pdfkeywords={HPC, HPCOps, Urban building, City Energy Simulation},
    bookmarksnumbered,bookmarksopen,linktocpage,
    colorlinks=true,
    citecolor=CustomBlue,
    linkcolor=CustomBlue,
    urlcolor=blue
}

@@

@@

\tableofcontents
\listoffigures
%\listoftables

\section{Introduction}
\label{sec:introduction}

The building sector accounts for approximately 40\% of final energy consumption and 36\% of greenhouse gas emissions within the European Union~\cite{european_commision_energy_2020}. In response, the EU has established ambitious targets under the Horizon 2050 framework to double energy renovation rates over the next decade~\cite{european_commision_stakeholder_2021}, highlighting the need for innovative solutions to drive these initiatives forward. The Centre of Excellence (CoE) HiDALGO2 project, focusing on high-performance computing and advanced simulations, is at the forefront of tackling this challenge, mainly through its Urban Building pilot application.

@@

\section{Ktirio Urban Building Workflow}
\label{sec:kub-workflow}

@@

\subsection{Data Handling and Simulation Process}
\label{sec:data-handling}

The workflow begins with collecting and preparing GIS and weather data, transforming it into a format usable for simulations. This data is then partitioned for scalable processing and converted into Modelica and Feel++\cite{christophe_prudhomme_feelppfeelpp_2024} compatible formats through the UBEM Generator.

@@

\subsection{Final Analysis and Urban Scale Energy Evaluation}
\label{sec:final-analysis}

The final step involves the UBEM Simulator, which generates large-scale outputs that summarize the overall energy consumption and environmental impact of buildings on an urban scale. This comprehensive urban scale analysis merges data from the building energy and air quality models to provide a holistic view of urban environmental quality.

@@

\section{Overview of Urban Building Modeling and Simulation}
\label{sec:urban-building}
